Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-07-17 longSC.tex
Babara's comment minor ones

The temperature dependence of $\eta/s$ has some generic features that most known fluids obey. One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations also support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
%This may have important implications for other fundamental physics goals. 
It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed. The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. The systematic uncertainty from the centrality determination is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).

As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.

@@

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}. The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The fifth order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}
Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. First, we have compared our observables with event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%. However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges. 
While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out as predicted in ~\cite{Niemi:2012aj}.
The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to nonflow effects and independent of symmetry plane correlations.
We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in the initial stage. 
The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to capture the centrality dependence of higher order correlations. 
Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions. A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered. %Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
Together with the measurements of individual harmonics these results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.

>>>>

The temperature dependence of $\eta/s$ has some generic features that most known fluids obey. One such general behavior is that this ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy density ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be conjectured using AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations constrained by data support the view that $\eta/s$ of the QGP is close to that limit~\cite{Gale:2012rq}.
%This may have important implications for other fundamental physics goals. 
It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental study~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

The event centrality was determined by the V0 detectors \cite{Abbas:2013taa} with better than 2\%  resolution for the whole centrality range analyzed. The systematic uncertainty from the centrality determination was evaluated by using the TPC and Silicon Pixel Detector (SPD) \cite{Dellacasa:1999kf} detectors instead of the V0 detectors. 
The systematic uncertainty on the symmetric cumulants which arises from the centrality uncertainty is about 3\% both for SC(5,2) and SC(4,3), and 8\% for  SC(5,3).
As described in Sec.~\ref{sec:experiment}, the reconstructed vertex position along the beam axis ($z$-vertex) is required to be located within 10 cm of the interaction point (IP) to ensure uniform detector acceptance for tracks within $|\eta|<0.8$. The systematic uncertainty from the $z$-vertex cut was estimated by reducing the $z$-vertex range to 8~cm and was found to be less than 3\%.

@@

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we show the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this avoids large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from the $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. We use the notation $v_n$ instead of $v_{2}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The fifth order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}
Three different models are compared with the experimental results presented in Sec.~\ref{sec:results}. 
We compare to event-by-event EKRT+viscous hydrodynamics predictions with various parameterizations of the temperature dependence of $\eta/s(T)$; these were shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}.
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

The event-by-event EKRT+viscous hydrodynamic calculations are also compared to the data in Fig.~\ref{fig:Figure_6} and Fig.~\ref{fig:Figure_7}.
In the case of NSC(3,2), the hydrodynamic calculations underestimate the magnitude of the data as discussed in Sec.~\ref{sec:theory_allorder} and show very weak $p_{\rm T}$ dependence for all centralities.
The $p_{\rm T}$ dependence of NSC(3,2) is well captured by the model calculations in all collision centralities except for 40--50\% where the data shows stronger $p_{\rm T}$ dependence than the models. The difference between the model calculations with the two different parameterizations of $\eta/s(T)$ is very small. 
As for NSC(4,2), the model calculations overestimate the magnitude of the data in the 5--20\% centralities and underestimate it in the centrality range $>$~20\%. However, the $p_{\rm T}$ dependence is well described by the model calculations in all centrality ranges. 
While the difference of the model results for the two parameterizations in most centralities is rather small, a clear separation between the two are observed in the 10--20\% centrality range where both the magnitude and $p_{\rm T}$ dependence are different.

This observed moderate $p_{\rm T}$ dependence in mid-central collisions both for NSC(3,2) and NSC(4,2) might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out, as predicted in ~\cite{Niemi:2012aj}.
The comparisons to hydrodynamic models can further help to understand the viscous corrections to the momentum distributions at hadronic freeze-out~\cite{Dusling:2009df,Luzum:2010ad,Teaney:2012ke,Molnar:2014fva,Niemi:2015qia}.
%\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{} and VISH2+1 calculations~\cite{Zhu:2016puf}]}}

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlations between the higher order harmonics ($v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of the correlations between $v_3$ and $v_2$ and between $v_4$ and $v_2$.
The results are obtained with Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to nonflow effects and independent of symmetry plane correlations.
We have found that fluctuations of SC(3,2) and SC(4,3) are anti-correlated in all centralities while fluctuations of SC(4,2), SC(5,2) and SC(5,3) are correlated for all centralities. 
These measurements were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions on the final state particle anisotropies.
The sign of SC(3,2) in 0--10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which dominates in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in the initial stage. 
The comparisons to VISH2+1 calculations show that all the models with large $\eta/s$, regardless of the initial conditions, fail to capture the centrality dependence of higher order correlations. 
Based on the tested model parameters, the data favors small $\eta/s$ and the AMPT initial conditions. A quite clear separation of the correlation strength for different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
The default configuration of the AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most centralities and for most combinations of harmonics which were considered. %Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminate between theoretical models.
Finally, we have found that $v_3$ and $v_2$ as well as $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections to the equilibrium distribution at hadronic freeze-out.
Together with the measurements of individual harmonics these results can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
